%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Tecnobit (Tactical Communications Department)} % Organization
    {Valdepeñas, Spain} % Location
    {Apr. 2021 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of a Tactical Data Link processor, a multi-threaded Linux application using modern C++, unit testing and design patterns.}
        \item {Development of a Combat Management System (CMS) using QT and Luciad (GIS).}
        \item {Plan, organize and monitor tasks of the software development team. Mentoring of new members.}
        \item {Integration of communications systems such as network controller, modem, radio, GPS, NTP server, radar and cryptographic devices.}
        \item {Device integration through different interfaces: MIL-STD-1553, RS-232, RS-422, Ethernet and Moxa devices.}
        \item {Expertise in static and dynamic analysis tools such as Clang-Tidy, Cppcheck, AddressSanitizer and Valgrind. }
        \item {In-depth use of modern C++, STL, Boost, Qt, GoogleTest, TCP/IP communications and multi-threading.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Tecnobit (Optronic Systems Department)} % Organization
    {Valdepeñas, Spain} % Location
    {Jan. 2020 - Mar. 21} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Embedded software design and development in C/C++ using Xilinx SDK for Zynq board.}
        \item {Remote and on-site support to client.}
        \item {Controlling interfaces such as GPIO, I2C, UART and Ethernet.}
        \item {Customization of Yocto image.}
        \item {CI of SW components.}
        \item {Technologies used include C++14, STL, GoogleTest, Xilinx SDK, Yocto Project and Jenkins.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Tecnobit (Tactical Communications Department)} % Organization
    {Valdepeñas, Spain} % Location
    {Jun. 2014 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of a Tactical Data Link processor, a multi-threaded Linux application using modern C++, unit testing and design patterns.}
        \item {Development of a Combat Management System (CMS) using QT and Luciad (GIS).}
        \item {Design, develop and testing of Tactical Data Link Systems including Link11, Link16, Link22, JREAP and SIMPLE protocols.}
        \item {Network routing through Ethernet, radio and satellite. Technologies used include SNMP, iptables, firewalls, TCP, UDP and multicast.}
        \item {On-site system deployment, testing, support and training for navy members on ships, ground stations and aircrafts.}
        \item {Sockets programming with POSIX API and Boost.Asio.}
        \item {Port a VxWorks Tactical Data Link processor application to Linux.}
        \item {Technologies used include C++11 and Qt.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {VISILAB Research Group (University of Castilla - La Mancha)} % Organization
    {Ciudad Real, Spain} % Location
    {Sep. 2012 - May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and develop computer vision applications for desktop, Android and iOS platforms using OpenCV.}
        \item {[Book] OpenCV Essentials, Packt Publishing, 2014.}
        \item {[Article] A Vision-Based Localization Algorithm for an Indoor Navigation App, Eighth International Conference on Next Generation Mobile Apps, Services and Technologies (NGMAST), 2014.}
      \end{cvitems}
    }




%---------------------------------------------------------
\end{cventries}
